\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newcommand{\srg}{\operatorname{srg}}
\newcommand{\hash}[2]{\texttt{#1}\newline\texttt{#2}}
\newcommand{\codepath}[1]{\texttt{\detokenize{#1}}}

\title{No vertex of a Conway 99-graph has 17 or more Paley-perfect fibers}
\author{Machine-certified theorem note from the R230/g2prime artifacts}
\date{July 5, 2026}

\begin{document}
\maketitle

\begin{abstract}
This note records the certificate chain proving that, subject to the standard
faithfulness of the honest rooted CNF base, no strongly regular graph
\(\srg(99,14,1,2)\) has a vertex at which at least \(17\) of its \(21\)
rooted fibers induce the Paley/C4 pattern.  The new machine-certified content
is local to one root: six \(k=20\) completion certificates and twenty-four
\(k=19\) two-exceptional-fiber certificates, plus the \(k=18\) triple
completion layer (seventy-two per-fiber defect certificates and one joint
residual certificate), plus the \(k=17\) four-exceptional completion layer:
fifty-four per-fiber forcing certificates across nine forcing orbit-types and
one joint \(C_4\)-cycle residual certificate.  All \(158\) listed local
certificate instances are UNSAT by CaDiCaL and independently checked by
\codepath{drat-trim}; the \(k=18\) triangle residual is also independently
UNSAT by CMS+XOR, and the \(k=17\) \(C_4\)-cycle residual is additionally
re-confirmed by \codepath{lrat-check} and by CMS+XOR with forced Gaussian
elimination.  The use of R230 is the already certified statement that no single
vertex has all \(21\) Paley-perfect fibers.  This is not an unconditional
nonexistence proof for Conway's \(\srg(99,14,1,2)\) problem.
\end{abstract}

\section{The statement}

\begin{theorem}[rooted \(k \geq 17\) exclusion]
\label{thm:k17}
Assuming the honest rooted CNF base faithfully encodes the rooted
\(\srg(99,14,1,2)\) equations stated in Section~\ref{sec:base}, no strongly
regular graph \(\srg(99,14,1,2)\) has a vertex at which \(\geq 17\) of its
\(21\) rooted fibers induce a \(C_4\).
\end{theorem}

Equivalently, no vertex is ``\(17\)-of-\(21\) Paley-perfect''.  This strictly
strengthens the published every-vertex Paley-pattern obstruction of Makhnev
1988, condition \((*)\), and the repository-local R230 certificate excluding a
single fully Paley-perfect vertex with all \(21\) fibers.

The theorem is claim-bearing but deliberately scoped.  It proves neither
unconditional nonexistence of \(\srg(99,14,1,2)\) nor the absence of vertices
with at most \(16\) Paley-perfect fibers.

\section{Rooted setup and fibers}
\label{sec:setup}

Let \(G\) be a hypothetical \(\srg(99,14,1,2)\), and root at a vertex \(r\).
Since \(\lambda=1\), the neighborhood \(N(r)\) is a perfect matching on
\(14\) vertices.  Label its matched pairs
\[
  \{0,1\},\{2,3\},\ldots,\{12,13\}, \qquad \bar x=x\oplus 1.
\]
A vertex at distance two from \(r\) is adjacent to exactly two vertices of
\(N(r)\), by \(\mu=2\), and these two local neighbors cannot be matched to
each other.  Thus the \(84\) far vertices are labelled by pairs
\[
  (a,b), \qquad 0\leq a<b<14,\qquad b\neq \bar a.
\]

The two matched-pair indices appearing in a label define a fiber.  There are
\(\binom 72=21\) fibers, each containing four far vertices.  If a fiber is on
matched pairs \(P=\{p_0,p_1\}\) and \(Q=\{q_0,q_1\}\), its four far labels are
\((p_i,q_j)\).  The fiber is \(C_4\), or Paley-perfect, when the four
share-one-local pairs are edges and the two opposite-corner pairs are nonedges.
A vertex is Paley-perfect when all \(21\) rooted fibers are \(C_4\).  R230
certifies that no such vertex exists.

\section{The honest rooted base}
\label{sec:base}

The certificates in this note use the base generated by
\codepath{scratchpad/honest_flip_cnf.py:build_base_cnf}, with labels from
\codepath{source/root_cell_cpsat.py:make_labels(14)}.  The recorded base has
\[
84\text{ far vertices},\quad 3486\text{ far-edge variables},\quad
285852\text{ product variables},\quad 1375458\text{ CNF variables},
\]
and \(3109092\) base clauses.  It encodes the following rooted equations.

First, every far vertex has far degree \(12\):
\[
  \sum_{j\neq i} e_{ij}=12.
\]
Second, the local-far \(\lambda/\mu\) quota equations, called \(P2\) here, are
\[
  \sum_{\substack{j\neq i\\ x\in L_j}} e_{ij}
  =2-\mathbf 1_{x\in L_i}-\mathbf 1_{\bar x\in L_i}
\]
for every far label \(L_i\) and local vertex \(x\).  Third, the far-far
\(\lambda/\mu\) equations, called \(P3\) here, are
\[
  \sum_{z\neq i,j} e_{iz}e_{jz}+e_{ij}=2-\lvert L_i\cap L_j\rvert .
\]
The product terms \(e_{iz}e_{jz}\) are Tseitin-encoded by auxiliary variables.
These are the standing faithfulness assumptions for the certificate, the same
kind of assumption used in R230.  The proof-checking below certifies the
derived CNFs; it does not replace the human audit that these equations are the
intended rooted SRG equations.

\section{Fiber completion}
\label{sec:completion}

\begin{lemma}[Fiber Completion Lemma]
\label{lem:completion}
In the honest rooted system, if \(20\) of the \(21\) rooted fibers are asserted
to be \(C_4\), then the remaining fiber is forced to be exactly \(C_4\).
\end{lemma}

In the canonical representative, the remaining fiber is
\[
F_0=\{(0,2),(0,3),(1,2),(1,3)\}.
\]
The audit asserts only the \(80\) C4-edge units from the other \(20\) fibers.
Unit propagation on the real base forces
\[
(0,2)(0,3),\ (1,2)(1,3),\ (0,2)(1,2),\ (0,3)(1,3)
\]
to be edges, and forces the diagonals
\[
(0,2)(1,3),\ (0,3)(1,2)
\]
to be nonedges.  This BCP-level statement is recorded in
\codepath{scratchpad/.work/g2prime_audit_v2.md}, Section 3, and is certified again
by the six DRAT-checked defect certificates in
\codepath{scratchpad/ladder/g2prime/final/}.

The pen-and-paper mechanism is the matching argument from the same audit.  For
a local vertex \(x\), the \(12\) far vertices whose labels contain \(x\) must
pair up by share-\(x\) edges, because \(N(x)\) is a perfect matching.  If all
fibers except \(F_0\) are \(C_4\), then the five good fibers through the
relevant matched pair already provide five disjoint share-\(x\) edges, covering
ten of those twelve vertices.  The two remaining vertices are the two
\(F_0\)-vertices containing \(x\), so they must be paired.  Running this at
\(x=0,1,2,3\) forces the four C4 edges of \(F_0\).  Those forced edges then
saturate the \(P2\) quotas and block both diagonals.

\begin{proposition}[Two-exceptional completion, \(k=19\)]
\label{prop:k19}
In the honest rooted system, if \(19\) fibers are asserted to be \(C_4\), then
the two remaining fibers are also forced to be \(C_4\).
\end{proposition}

The \(210=\binom{21}{2}\) possible pairs of exceptional fibers split under the
rooted \(S_7\) action into two orbits: \(105\) disjoint pairs and \(105\)
intersecting pairs.  Representatives are
\[
\{(0,1),(2,3)\}\quad\text{and}\quad \{(0,1),(0,2)\}.
\]
For each representative, the \(19\) good fibers contribute \(76\) C4-edge unit
premises.  The certificate table
\codepath{certificates/rep_table_k19.json} lists every single
defect on either exceptional fiber: absence of one of the four C4 edges, or
presence of one of the two diagonals.  Each such defect plus the \(76\) good
units is UNSAT and DRAT-verified; the manifest lists \(24\) explicit
certificates, \(12\) for each orbit.  Since a non-\(C_4\) fiber must have one
of these defects, no defect is possible.

\begin{proposition}[Triple-exceptional completion, \(k=18\)]
\label{prop:k18}
In the honest rooted system, if \(18\) fibers are asserted to be \(C_4\),
then the three remaining fibers cannot all be non-\(C_4\).
\end{proposition}

The \(1330=\binom{21}{3}\) triples of exceptional fibers are the \(3\)-edge
graphs on the seven matched-pair indices.  Under the rooted \(S_7\) action
they split into five orbit-types:
\begin{center}
\codepath{star_K1_3}, \codepath{path_P4}, \codepath{P3_plus_edge},
\codepath{three_matching}, \codepath{triangle_K3}.
\end{center}
The first four orbit-types are closed by per-fiber defect certificates.  In
each representative, the \(18\) good fibers contribute \(72\) C4-edge unit
premises.  For each exceptional fiber, each of the six possible defects
-- absence of one of its four C4 edges, or presence of one of its two
diagonals -- is refuted by the base plus those \(72\) units.  The manifest
\codepath{certificates/k18/manifest_k18A.json} records \(72\) such
certificates in total:
\[
4\text{ orbit-types}\times 3\text{ fibers}\times 6\text{ defects}=72.
\]
The solve log \codepath{certificates/k18/solve_k18A_results.txt} records every
one as \(\texttt{s UNSATISFIABLE}\) by CaDiCaL and
\(\texttt{s VERIFIED}\) by \codepath{drat-trim}.

The fifth orbit-type is the index triangle
\[
\{\{0,1\},\{0,2\},\{1,2\}\}.
\]
Here the per-fiber mechanism does not apply: with only the \(72\) good-fiber
units asserted, BCP does not force any one of the three triangle fibers to be
\(C_4\).  The residual is therefore posed jointly.  It is the honest base plus
the \(72\) good-fiber unit clauses for the triangle representative, plus one
six-literal ``non-\(C_4\)'' disjunction for each of the three triangle fibers.
Each such disjunction says: at least one of the four C4 edges is absent, or at
least one of the two diagonals is present.  The exact clauses are recorded in
\codepath{certificates/k18/manifest_k18B.json}.

This joint residual instance,
\[
\text{base}+72\text{ good units}+3\text{ non-}C_4\text{ clauses},
\]
is UNSAT: \codepath{certificates/k18/residual_verdict.txt} records CaDiCaL
UNSAT in \(16.7\) seconds, \codepath{drat-trim} VERIFIED with a \(205\) MB
proof, and an independent CMS+XOR UNSAT verdict.  Its meaning is narrower than
per-fiber forcing.  It says that, once the other \(18\) fibers are \(C_4\), the
three index-triangle fibers cannot all be non-\(C_4\).  Therefore at least one
index-triangle fiber is \(C_4\), giving at least \(19\) \(C_4\) fibers and
reducing the case to Proposition~\ref{prop:k19}.  The vacuity control
\[
\text{base}+72\text{ good units only}
\]
returned \(\texttt{UNKNOWN(timeout)}\) at \(900\) seconds, so the three
non-\(C_4\) clauses carry the residual content.

\begin{proposition}[Four-exceptional completion, \(k=17\)]
\label{prop:k17}
In the honest rooted system, if \(17\) fibers are asserted to be \(C_4\),
then the four remaining fibers cannot all be non-\(C_4\).
\end{proposition}

The \(\binom{21}{4}=5985\) quadruples of exceptional fibers are the \(4\)-edge
graphs on the seven matched-pair indices.  Under the rooted \(S_7\) action they
split into exactly ten orbit-types, whose sizes sum to \(5985\).  Nine of the
ten orbit-types are closed by per-fiber forcing.  In each of these nine
representatives, the \(17\) good fibers contribute \(68\) C4-edge unit premises
(\(17\text{ good fibers}\times 4\text{ edges}=68\)), and at least one
exceptional fiber has each of its six possible defects
-- absence of one of its four C4 edges, or presence of one of its two diagonals
-- refuted by the base plus those \(68\) units, so that fiber is forced to be
\(C_4\), contradicting ``exactly \(17\)''.  The manifest
\codepath{certificates/k17/manifest_k17A.json} records \(54\) such
certificates in total:
\[
9\text{ orbit-types}\times 1\text{ forcing fiber}\times 6\text{ defects}=54.
\]
The solve log \codepath{certificates/k17/solve_k17A_results.txt} records every
one as \(\texttt{s UNSATISFIABLE}\) by CaDiCaL and
\(\texttt{s VERIFIED}\) by \codepath{drat-trim}, with the summary line
\(\texttt{k17A certs: PASS=54 FAIL=0}\).

The tenth orbit-type is the \(4\)-cycle \(\codepath{C4_cycle}\), with
exceptional fibers
\[
\{\{0,1\},\{0,2\},\{1,3\},\{2,3\}\}.
\]
Here the per-fiber mechanism does not apply: with only the \(68\) good-fiber
units asserted, BCP forces none of the four cycle fibers to be \(C_4\).  The
residual is therefore posed jointly.  It is the honest base plus the \(68\)
good-fiber unit clauses for the cycle representative, plus one six-literal
``non-\(C_4\)'' disjunction for each of the four cycle fibers.  Each such
disjunction says: at least one of the four C4 edges is absent, or at least one
of the two diagonals is present.  The exact clauses are recorded in
\codepath{certificates/k17/manifest_k17B.json}.

This joint residual instance,
\[
\text{base}+68\text{ good units}+4\text{ non-}C_4\text{ clauses},
\]
is UNSAT: \codepath{certificates/k17/residual_verdict.txt} records CaDiCaL
UNSAT in \(700\) seconds with a \(524\) MB DRAT proof, and \codepath{drat-trim}
VERIFIED (verification time \(803\) s; \(139977\) clauses and \(404332\) lemmas
in the core, \(30.8\)M resolution steps, \(12532\) RAT lemmas -- a genuine deep
proof).  It is independently re-confirmed by \codepath{cadical --lrat} plus
\codepath{lrat-check} (\(\texttt{c VERIFIED}\)) and by CMS+XOR with forced
Gaussian elimination (\(\texttt{s UNSATISFIABLE}\)).  Its meaning is narrower
than per-fiber forcing.  It says that, once the other \(17\) fibers are
\(C_4\), the four \(4\)-cycle fibers cannot all be non-\(C_4\).  Therefore at
least one \(4\)-cycle fiber is \(C_4\), giving at least \(18\) \(C_4\) fibers
and reducing the case to Proposition~\ref{prop:k18}.  The vacuity control
\[
\text{base}+68\text{ good units only}
\]
returned \(\texttt{UNKNOWN(timeout)}\) at \(900\) seconds (\(1.38\)M conflicts,
never UNSAT), so the four non-\(C_4\) clauses carry the residual content.

\section{Proof of Theorem~\ref{thm:k17}}

Suppose a rooted graph has at least \(17\) \(C_4\) fibers.  If it has exactly
\(17\), choose those \(17\) fibers.  Proposition~\ref{prop:k17} shows that the
four remaining fibers cannot all be non-\(C_4\), so the root has at least
\(18\) \(C_4\) fibers after all.  If it has exactly \(18\), choose those \(18\)
fibers.  Proposition~\ref{prop:k18} shows that the three remaining fibers
cannot all be non-\(C_4\), so the root has at least \(19\) \(C_4\) fibers.  If
it has at least \(19\), Proposition~\ref{prop:k19} forces all \(21\) fibers to
be \(C_4\).  In every case the root is Paley-perfect, contradicting R230, which
certifies that no \(\srg(99,14,1,2)\) has a single Paley-perfect vertex.

The \(k=20\) Fiber Completion Lemma is the one-exceptional special case and is
included because it supplies both the analytic mechanism and the independently
checked six-certificate rung immediately above \(k=19\).

\section{Certificate architecture}
\label{sec:certs}

The \(k=20\) certificates use the same base plus \(80\) good-fiber units and
one defect unit on the remaining fiber \(F_0\).  There are six explicit
certificates: four missing-C4-edge defects and two present-diagonal defects.
All six are solved by CaDiCaL as \(\texttt{s UNSATISFIABLE}\) and checked by
\codepath{drat-trim2.exe} as \(\texttt{s VERIFIED}\).  The proof files are genuine
propagation-sized DRATs, \(3486513\) to \(3486515\) bytes.  The vacuity control
\(\text{base}+\text{ce1 defect only}\), with the \(80\) good units removed,
returns \(\texttt{UNKNOWN(timeout)}\) at \(600\) seconds.

The \(k=19\) certificates use the same base plus \(76\) good-fiber units and
one defect unit on one of the two exceptional fibers.  There are \(24\)
explicit certificates: two exceptional-pair orbits, two exceptional fibers per
orbit, and six listed defect slots per fiber.  All \(24\) are solved by CaDiCaL
as \(\texttt{s UNSATISFIABLE}\) and checked by \codepath{drat-trim2.exe} as
\(\texttt{s VERIFIED}\).  The proof files are \(3486474\) to \(3486480\)
bytes.  The two vacuity controls, one for each exceptional-pair orbit, remove
the \(76\) good units and keep only a diagonal-presence defect; both return
\(\texttt{UNKNOWN(timeout)}\) at \(600\) seconds.

The \(k=18\) forcing certificates use the same base plus \(72\) good-fiber
units and one defect unit on one of three exceptional fibers.  There are \(72\)
explicit certificates for the four non-triangle triple orbits, all solved by
CaDiCaL as \(\texttt{s UNSATISFIABLE}\) and checked by
\codepath{drat-trim2.exe} as \(\texttt{s VERIFIED}\).  The residual
\codepath{k18B_residual_triangle.cnf} is a single joint instance for the
triangle orbit: base, \(72\) good units, and the three six-literal non-\(C_4\)
clauses.  It is CaDiCaL UNSAT in \(16.7\) seconds and DRAT-verified with a
\(205\) MB proof; CMS+XOR independently reports UNSAT.  Its vacuity control
removes the three non-\(C_4\) clauses and leaves base plus \(72\) good units;
that control returns \(\texttt{UNKNOWN(timeout)}\) at \(900\) seconds.

The \(k=17\) forcing certificates use the same base plus \(68\) good-fiber
units and one defect unit on one of four exceptional fibers.  There are \(54\)
explicit certificates for the nine forcing quadruple orbits, all solved by
CaDiCaL as \(\texttt{s UNSATISFIABLE}\) and checked by
\codepath{drat-trim} as \(\texttt{s VERIFIED}\); the solve log records
\(\texttt{k17A certs: PASS=54 FAIL=0}\).  The residual is a single joint
instance for the \(\codepath{C4_cycle}\) orbit: base, \(68\) good units, and
the four six-literal non-\(C_4\) clauses.  It is CaDiCaL UNSAT in \(700\)
seconds with a \(524\) MB DRAT proof, and \codepath{drat-trim} VERIFIED in
\(803\) seconds (\(139977\) core clauses, \(404332\) lemmas, \(30.8\)M
resolution steps, \(12532\) RAT lemmas); \codepath{cadical --lrat} plus
\codepath{lrat-check} independently report \(\texttt{c VERIFIED}\), and CMS+XOR
with forced Gaussian elimination independently reports UNSAT.  Its vacuity
control removes the four non-\(C_4\) clauses and leaves base plus \(68\) good
units; that control returns \(\texttt{UNKNOWN(timeout)}\) at \(900\) seconds
(\(1.38\)M conflicts).

The symmetry wrappers are also explicit.  The final transitivity report records
one orbit on the \(21\) fibers, one orbit on the four C4-edge slots inside
\(F_0\), and one orbit on the two diagonals inside \(F_0\).  The \(k=19\) rep
table records the two pair-position orbits, disjoint and intersecting, of
sizes \(105\) and \(105\).  The \(k=18\) rep table records the five
triple-position orbits, of sizes \(140,420,630,105,35\).  These are the only
WLOG reductions used in this note.

\subsection*{Certificate count table}

\begin{center}
\begin{tabular}{>{\small}p{0.25\linewidth}>{\centering\arraybackslash}p{0.12\linewidth}p{0.38\linewidth}p{0.15\linewidth}}
\toprule
Rung & Instances & Recipe & Status\\
\midrule
\(k=20\) completion & 6 & base \(+80\) good units \(+1\) defect unit & UNSAT; DRAT VERIFIED\\
\(k=19\) two-exceptional & 24 & base \(+76\) good units \(+1\) defect unit & UNSAT; DRAT VERIFIED\\
\(k=18\) four forcing triple orbits & 72 & base \(+72\) good units \(+1\) defect unit & UNSAT; DRAT VERIFIED\\
\(k=18\) triangle residual & 1 & base \(+72\) good units \(+3\) non-\(C_4\) clauses & UNSAT; DRAT VERIFIED\\
\(k=17\) nine forcing quadruple orbits & 54 & base \(+68\) good units \(+1\) defect unit & UNSAT; DRAT VERIFIED\\
\(k=17\) \(C_4\)-cycle residual & 1 & base \(+68\) good units \(+4\) non-\(C_4\) clauses & UNSAT; DRAT VERIFIED\\
\midrule
Total local instances in the reproducer & 158 & \multicolumn{2}{l}{All SHA-checked from the committed recipe.}\\
\bottomrule
\end{tabular}
\end{center}

\subsection*{\(k=20\) certificate table}

\scriptsize
\begin{longtable}{>{\ttfamily}p{0.15\linewidth}p{0.23\linewidth}p{0.39\linewidth}p{0.18\linewidth}}
\toprule
Cert & File/defect & SHA-256 & Status\\
\midrule
\endfirsthead
\toprule
Cert & File/defect & SHA-256 & Status\\
\midrule
\endhead
cd1 & \codepath{certfull_cd1.cnf}: diagonal present \((0,2)-(1,3)\) & \hash{c2f4e89d0c1462e48fcb7deade1e6e98}{564d97758684543652170273a3090408} & UNSAT; DRAT VERIFIED \\
cd2 & \codepath{certfull_cd2.cnf}: diagonal present \((0,3)-(1,2)\) & \hash{99bd47880036988066003e193ae749ea}{d6414faf6c5ae8164c014f2e0e8e1fb7} & UNSAT; DRAT VERIFIED \\
ce1 & \codepath{certfull_ce1.cnf}: C4 edge absent \((0,2)-(0,3)\) & \hash{132e2b3746dbd5491b66b7b30f3d04ad}{12ac8d727b49b66d2c6ec9a618d86057} & UNSAT; DRAT VERIFIED \\
ce2 & \codepath{certfull_ce2.cnf}: C4 edge absent \((1,2)-(1,3)\) & \hash{e74fc7ca3f9c4b848f05d057592f24ec}{69044bf6b38f885ae2965b3af7735591} & UNSAT; DRAT VERIFIED \\
ce3 & \codepath{certfull_ce3.cnf}: C4 edge absent \((0,2)-(1,2)\) & \hash{d269f00feddbd633d3ffc54a7b402fa3}{8e21ae56607f3d09c159cca02636e10c} & UNSAT; DRAT VERIFIED \\
ce4 & \codepath{certfull_ce4.cnf}: C4 edge absent \((0,3)-(1,3)\) & \hash{723491e312f3f16ac274d2dd61973faa}{16596e8a3a359e3d5f520cd7fcb362bc} & UNSAT; DRAT VERIFIED \\
\bottomrule
\end{longtable}
\normalsize

\subsection*{\(k=19\) certificate table}

\scriptsize
\begin{longtable}{>{\ttfamily}p{0.22\linewidth}p{0.12\linewidth}p{0.16\linewidth}p{0.31\linewidth}p{0.14\linewidth}}
\toprule
File & Orbit & Defect & SHA-256 & Status\\
\midrule
\endfirsthead
\toprule
File & Orbit & Defect & SHA-256 & Status\\
\midrule
\endhead
k19\_disjoint\_01.cnf & disjoint & c4\_edge\_absent & \hash{c47f831b066e637d6a9cf05903c3b12c}{27499d35abf8c560b4755b866fd1c082} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_02.cnf & disjoint & c4\_edge\_absent & \hash{6b417f909944f75233b7961505a5fe8e}{afea45bb009ce8c1ed68de9255835eb4} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_03.cnf & disjoint & c4\_edge\_absent & \hash{8dc4f908f0758a929090d68899c34198}{7527b1e2396300613bca70e72f932cb3} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_04.cnf & disjoint & c4\_edge\_absent & \hash{9fd5674f15950869933142b4eb5e0baf}{2e4ba6c90c7a9c28da416198dd1a593c} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_05.cnf & disjoint & diagonal\_present & \hash{75f6b8c15783fca140b85551c21fa731}{be413b05a696a71871f1046f4e7799d3} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_06.cnf & disjoint & diagonal\_present & \hash{a74ae8f2c497227a26c38790e578251c}{e86f92101791c76667a25ae15c52139a} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_07.cnf & disjoint & c4\_edge\_absent & \hash{84cfdc1ec7d199dc1379109f37165dbe}{f07e82a509ad6044c901e173866f6110} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_08.cnf & disjoint & c4\_edge\_absent & \hash{5a4fe45fad08bf644a9f4da14fe7cc45}{7c1b07a5895c1def7abb6b216433c462} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_09.cnf & disjoint & c4\_edge\_absent & \hash{0bd5710781f79b7bd3cde3f234714057}{cb2a49b52c3dd19c7f01bb35402fe4f2} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_10.cnf & disjoint & c4\_edge\_absent & \hash{02f663ee10d314d5d70ab83a2913f9e8}{9b79b61d706079b476cfbb0e6f9c7e2e} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_11.cnf & disjoint & diagonal\_present & \hash{ed165fd310a9bc2e99dab3f2479cb58a}{3d4098c3c2cd18bd09d72063a8e5a77a} & UNSAT; DRAT VERIFIED \\
k19\_disjoint\_12.cnf & disjoint & diagonal\_present & \hash{617cb9bf99a3b48683123ca08cc68293}{fc2a6db9bc6f0fb41d34c156c8d3aa0e} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_01.cnf & intersect & c4\_edge\_absent & \hash{286e3acff2c5e105e429bcba91b7efc3}{cdcfa27d9b13164807d5809734511ac8} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_02.cnf & intersect & c4\_edge\_absent & \hash{ab4e4f5a9025b8f0095ff3dda66db254}{2b85d8f22a57ff88421b137ad1cc7d99} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_03.cnf & intersect & c4\_edge\_absent & \hash{f72d6f3212461e010b742f19a2d4b044}{e74894caa747befbe81be2ae8d60fd98} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_04.cnf & intersect & c4\_edge\_absent & \hash{7e1a344b7216678d7e5a886565acf376}{be8f4f1aae76bd1a743b575a83208a6d} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_05.cnf & intersect & diagonal\_present & \hash{3e8a594895b20348b5717a687af04cd4}{06fd564025e253d4764289b9199bbf4e} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_06.cnf & intersect & diagonal\_present & \hash{c04025fb0675628651052676975ee35f}{cf4d55fec45681d883fc8960c47d3eb3} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_07.cnf & intersect & c4\_edge\_absent & \hash{ed7dfb5b2c9272f1b360eac996a06173}{0288dfd395dcd32619c393fafedc809d} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_08.cnf & intersect & c4\_edge\_absent & \hash{4e1114e057b5d8c3343e05954c86c09c}{1bc8f622d9ac6192ec3b5fc4de544edd} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_09.cnf & intersect & c4\_edge\_absent & \hash{a77215ec2ee4e1ee0cda21ae89f04414}{55ce4c9faa8a3a4202d1af57416db127} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_10.cnf & intersect & c4\_edge\_absent & \hash{5eedfcc0503492ad62ae051f3580a6c8}{0f663b2f39393d0f46480e00a7bba1ca} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_11.cnf & intersect & diagonal\_present & \hash{82aeebf1f592a64544db2f1e6e9ed8af}{19e9ea34e03968b11e0800048a3bcf8a} & UNSAT; DRAT VERIFIED \\
k19\_intersect\_12.cnf & intersect & diagonal\_present & \hash{aa04a2351d7481cdb9a1ed669d42b5a6}{880b232b0067eb111b21f30c7717ee6d} & UNSAT; DRAT VERIFIED \\
\bottomrule
\end{longtable}
\normalsize

\section{What is certified, cited, and still open}

Machine-certified in this repository:
\begin{itemize}
\item R230: no single Paley-perfect vertex with all \(21\) fibers \(C_4\), via
  \(24\) orbit representatives, all UNSAT and independently DRAT-verified.
\item The \(k=20\) Fiber Completion Lemma: \(80\) good-fiber units force the
  remaining fiber, with six explicit defect certificates and a \(600\)-second
  vacuity control.
\item The \(k=19\) two-exceptional extension: \(76\) good-fiber units force
  both remaining fibers, with \(24\) explicit defect certificates and two
  \(600\)-second vacuity controls.
\item The \(k=18\) triple-exceptional extension: four triple orbits are closed
  by \(72\) per-fiber defect certificates, and the triangle orbit is closed by
  one joint residual certificate plus a \(900\)-second vacuity control.
\item The \(k=17\) four-exceptional extension: nine quadruple orbit-types are
  closed by \(54\) per-fiber forcing certificates, and the \(C_4\)-cycle orbit
  is closed by one joint residual certificate (triple-verified by
  \codepath{drat-trim}, \codepath{lrat-check}, and CMS+XOR-Gauss) plus a
  \(900\)-second vacuity control.
\item The symmetry reductions used here: the \(21\) fibers form one orbit; the
  two exceptional-fiber-pair types are exactly disjoint and intersecting; the
  five exceptional-fiber-triple types are exactly
  \codepath{star_K1_3}, \codepath{path_P4}, \codepath{P3_plus_edge},
  \codepath{three_matching}, and \codepath{triangle_K3}.
\end{itemize}

Cited, not reproved here:
\begin{itemize}
\item Makhnev 1988 proves that no \(\srg(99,14,1,2)\) satisfies condition
  \((*)\), the every-vertex Paley-perfect hypothesis.
\item Keramatipour 2023 gives an independent modern no-global-Paley-pattern
  result.
\item Cesarz--Woldar record that the existence of a single Paley graph of order
  \(9\) inside a putative Conway 99-graph was unclear in the literature.
\end{itemize}

Open or not claimed:
\begin{itemize}
\item Conway's problem remains open.  This note does not rule out an
  \(\srg(99,14,1,2)\) in which every vertex has at most \(16\) \(C_4\) fibers.
\item The \(k\leq 16\) range is open.
\item The base-encoding faithfulness remains the standing assumption.  The
  DRAT proofs check the emitted CNFs; the mathematical link from a hypothetical
  graph to those CNFs rests on the rooted label model and the \(P2/P3\)
  equations stated above.
\end{itemize}

\section*{Source artifacts}

The load-bearing artifacts read for this note are:
\begin{center}
\begin{tabular}{>{\small}p{0.58\linewidth}p{0.34\linewidth}}
\codepath{scratchpad/.work/g2prime_audit_v2.md} & Fiber Completion Lemma and audit\\
\codepath{scratchpad/.work/makhnev_k20_report.md} & Makhnev context and corrected \(k=20\) history\\
\codepath{certificates/manifest_certfull.json} & \(k=20\) hashes and units\\
\codepath{certificates/solve_all_results.txt} & \(k=20\) solve/check status\\
\codepath{certificates/transitivity_report.json} & Fiber and slot transitivity\\
\codepath{certificates/rep_table_k19.json} & \(k=19\) orbit and defect table\\
\codepath{certificates/manifest_k19.json} & \(k=19\) hashes\\
\codepath{certificates/solve_k19_results.txt} & \(k=19\) solve/check status\\
\codepath{certificates/k18/rep_table_k18.json} & \(k=18\) triple-orbit table and residual encoding\\
\codepath{certificates/k18/manifest_k18A.json} & \(k=18\) forcing certificate hashes\\
\codepath{certificates/k18/solve_k18A_results.txt} & \(k=18\) forcing solve/check status\\
\codepath{certificates/k18/manifest_k18B.json} & \(k=18\) triangle residual hash and clauses\\
\codepath{certificates/k18/residual_verdict.txt} & \(k=18\) residual solve/check status\\
\codepath{certificates/k17/rep_table_k17.json} & \(k=17\) quadruple-orbit table and residual encoding\\
\codepath{certificates/k17/manifest_k17A.json} & \(k=17\) forcing certificate hashes\\
\codepath{certificates/k17/solve_k17A_results.txt} & \(k=17\) forcing solve/check status\\
\codepath{certificates/k17/manifest_k17B.json} & \(k=17\) \(C_4\)-cycle residual hash and clauses\\
\codepath{certificates/k17/residual_verdict.txt} & \(k=17\) residual solve/check status\\
\codepath{reports/FINAL_REPORT_R230_NONEXISTENCE.md} & R230 theorem and limitation\\
\codepath{../literature/README.md} & Published-literature index
\end{tabular}
\end{center}

\end{document}
